Current and future constraints on primordial magnetic fields

### 2015-11-13 pmf.tex
ii

We present new limits on the amplitude of any primordial magnetic field (PMF) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol. 
We reduce six-fold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 2.0\tbd{XX}$ from Planck alone to $\apmf < 0.33$ for the combined dataset at 95\% CL. 
Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
We also consider future limits from stage III CMB experiments (like \sptnew{},  \advactpol, or the \simons) and a stage IV concept. 
Stage III experiments will reduce the current limit by an additional factor of \tbd{XX}; this will become a factor of \tbd{XX} for stage IV. 
\tbd{maybe:} The constraints from a stage IV experiment have the potential to rule out much of the parameter space for PMFs. \tbd{really if could rule out them as explanation for galaxy fields... is there a lower bound for them to be useful?}

@@

Parity-violating processes

However, CMB polarization data are expected to improve constraints on extensions

of precision measurements of CMB polarization. 
CMB polarization opens up

we are beginning a new era of precision measurements of CMB polarization.

These measurements are now being extended to CMB polarization

one of the main pillars of the standard cosmolog
Precision measurements of cosmic microwave background (CMB) polarization open up new tests for extensions to the  standard cosmological model. 
Such extensions include the

>>>>

We present new limits on the amplitude of any primordial magnetic field (PMF) using temperature and polarization measurements of the cosmic microwave background (CMB)  from \planck{}, \bicepkeck{}, \pb, and \sptpol. 
We reduce six-fold the upper limit on the CMB anisotropy power due to a PMF, from $\apmf < 0.73$ from Planck alone to $\apmf < 0.30$ for the combined dataset at 95\% CL. 
Most of the improvement is due to the addition of the \bicepkeck{} data; without these bandpowers, the combined limit weakens to $\apmf < 0.\tbd{XX}$. 
We also consider future limits from stage III CMB experiments (like \sptnew{},  \advactpol, or the \simons) and a stage IV concept. 
Stage III experiments will reduce the current limit by an additional factor of \tbd{XX}; this will become a factor of \tbd{XX} for stage IV. 
\tbd{maybe:} The constraints from a stage IV experiment have the potential to rule out much of the parameter space for PMFs. \tbd{really if could rule out them as explanation for galaxy fields... is there a lower bound for them to be useful?}

@@

Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from galaxies and galaxy clusters \citep[for review, see][]{ryu12, widrow12}. 
There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although alternative explanations \citep{broderick12} have been proposed. 
High energy $\gamma$-rays can interact with IR-optical photons and produce electron-positron pairs. 
These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
Intergalactic magnetic fields could explain this by deflecting the particles.

recent results
